The Local Group in the Cosmic Web

### 2014-08-13 paper/main.tex
nuevas referencias, grandes cambios en la discusion

\title{The Expected Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}

@@

This tensor is real and symmetric, which means that it can be
diagonalized. 
We denote its eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. 
The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. 
If
the three, two, one or zero eigenvalues are larger than this threshold
the region is classified as peak, filament, sheet or void,
respectively.

@@

The algorithm to compute the potential is grid based. 
First we interpolate the density into a cubic grid with a
Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel. 
Then we obtain the gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. 
In our case we have used a grid size and a gaussian smoothing with
two times larger as the typical separation between the two halos in the Local Group. 
The purpose of this choice is to have both halos in the pair a common
environment. 
In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. 
The scale for the gaussian smoothing uses the same value.

@@

We find that the difference between the GS and the RS 
can be explained by the total pair mass.
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
amples is very narrow and it is used to constraint the LG mass.
We show in Table \ref{table:web_type} that a subset of the GS
having a similar mass range than the RS reproduces similar environment
fractions.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web in which they reside, as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
have shown that the local overdensity is the dominant web parameter
that define the abundance and properties of halos. Other quantities
derived from the tidal tensor play a secondary role defining
properties such as its formation history.

In our case, the fact that the preferred LG total mass is around
$1-4\times 10^{12}$\Msun $\,$implies that the preferred environment are
filaments and sheets with an overdensity close to the average
value. 
Correspondignly, the values for the ellipticity and prolateness are
also well defined for the LG pairs given its correlation with the
total mass.

@@

However, the alignments with the cosmic web that are not
mass dependent and seem to be stronger once the kinematic constraints
are imposed on the GS pairs. There is a clear anti-alignment between
the third eigenvector and the orbital angular momentum vector, meaning
that this vector is perpendicular to filaments and the sheets,  We
also found that the vector joining the LG halos are aligned with the
third eigenvector. This means that he pair is aligned with the filaments and
lies on the sheets and its motion is done along these directions.

@@

The most interesting feature is that these alignments are
tighter as we narrow the kinematic conditions of the LG towards the
observed values. A deeper understanding requires the study of the full
formation history and coevolution with the cosmic web, a task beyond
the scope of the work presented here.
However, such alignments can be traced in observations by looking for 
similar pairs samples (or even a more unconstrained pair sample) in galaxy surveys and study the angle between
pair axis and surrounding filament computed using a filament finder, 
such as codes presented by \citet{2010MNRAS.407.1449G,2011MNRAS.414..350S}.

These alignments for the LG pairs could be in contradiction with
recent findings \citep{2014MNRAS.443.1274L} that report a universal
trend where the eigenvector $\hat{e}_{3}$ marks the infall direction
for substructures. For the Milky Way its satellites are located at
high galactic latitudes, almost perpendicular to the vector pointing towards
the Andromeda Galaxy, which is the direction that we find aligned with
$\hat{e}_3$.

If the alignment we find in this paper holds, this would imply that
infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
in contradiction to the universal principle of
\citep{2014MNRAS.443.1274L}. If the universal accretion alignment
holds, that would imply that that the Andromeda galaxy is located
perpendicular to $\hat{e}_3$, in contradiction with the strong
alignment found in this paper. It would be desirable to have a
measurement of the cosmic web in the Local Universe to disentangle
this potential contradiction between different alignments and
understading the detailed properties of the LG in an explicit
cosmological context.

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments.
\bibliographystyle{apj}
\bibliography{references}

>>>>

\title{The Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}

@@

This tensor is real and symmetric, which means that it can be
diagonalized. 
We denote its eigenvalues as $\lambda_1\geq \lambda_2\geq
\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
$\hat{e}_2$ and $\hat{e}_3$. 
The web classification compares each one
of the three eigenvalues to a threshold value $\lambda_{\rm th}$. 
If
the three, two, one or zero eigenvalues are larger than this threshold
the region is classified as peak, filament, sheet or void,
respectively.  Because this tensor is also known as the tidal tensor
we refer to it as the Tweb algorithm.

@@

The algorithm to compute the potential is grid based. 
First we interpolate the mass into a cubic grid with a
Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel in order to reduce the grid influence in the computations that follow. 
Then we obtain the gravitational potential using FFT methods and use finite differences
to compute the Hessian at every point in the grid. 
In our case we have used a grid size and a gaussian smoothing with
two times larger as the typical separation between the two halos in the Local Group. 
The purpose of this choice is to have both halos in the pair a common
environment. 
In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
corresponding to a $256^3$ grid in the Bolshoi volume. 
The scale for the gaussian smoothing uses the same value.

@@

We find that the difference between the GS and the RS 
can be explained by the total pair mass.
In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
amples is very narrow and it is used to constraint the LG mass.
We show in Table \ref{table:web_type} that a subset of the GS
having a similar mass range than the RS reproduces similar environment
fractions. The correlation betwen halo mass and their environment is a
well known result \citep{1998ApJ...500...14L}.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web in which they reside, as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. This
confirms that the local overdensity, the trace of the tidal tensor,
is the dominant web parameter that define the abundance and properties
of halos 
\citep{1998ApJ...500...14L,1999MNRAS.302..111L,2004MNRAS.350.1385S,2009MNRAS.394.1825F,
  Alonso2014}. Other
quantities derived from the tidal tensor play a secondary role
defining properties such as its formation history.

In our case, the fact that the preferred LG total mass is around
$1-4\times 10^{12}$\Msun $\,$implies that the preferred environment are
filaments and sheets with an overdensity close to the average
value. 
Correspondingly, the values for the ellipticity and prolateness are
also well defined for the LG pairs given its correlation with the
total mass.

@@

However, the alignments with the cosmic web are 
mass-independent and seem to be stronger once the kinematic constraints
are imposed on the GS pairs. There is a clear anti-alignment between
the third eigenvector and the orbital angular momentum vector, meaning
that this vector is perpendicular to filaments and the sheets,  We
also found that the vector joining the LG halos are aligned with the
third eigenvector. This means that he pair is aligned with the filaments and
lies on the sheets and its motion is done along these directions.

@@

The most interesting feature is that these alignments are
tighter as we narrow the kinematic conditions of the LG towards the
observed values. A deeper understanding requires the study of the full
formation history and coevolution with the cosmic web, a task beyond
the scope of the work presented here.

These alignments for the LG pairs could be in contradiction with
findings
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
that report a universal trend where the eigenvector $\hat{e}_{3}$
(i.e. the filament direction) marks the infall direction for
substructures. The Milky Way satellites are located at high
galactic latitudes, almost perpendicular to the vector pointing
towards the Andromeda Galaxy, which is the direction that we find aligned with
$\hat{e}_3$.

If the alignment we find in this paper holds, this would imply that
infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
in contradiction to the accretion along filaments. If the universal accretion
along filaments holds, that would imply that that the Andromeda
galaxy is located perpendicular to $\hat{e}_3$, in contradiction with the strong
alignment found in this paper.

This apparent contradition can be solved if one considers that the
subhalo infall properties depend on the environment at {\it the
  merger time}, while the alignments for yet unvirialized pairs such as the LG
depend on the current state of the cosmic web. This also explain the absence
of a strong alignment with halo spin, because it reflects past
configurations of the web, not the current one. From this perspective,
a joint consideration of the alignments between the dominant
halos in the LG and their satellites, which also feature strong
signals \citep{2005A&A...431..517K,2013ApJ...766..120C}, should
inform us about the structural evolution of the cosmic web.

Our results also raise the need to observationally constrain
the alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
to select a LG sample to quantify the alignments with the filamentary
structure. 
This allows not only a direct quantification of how common are the LG
aligments but also provides a new test of $\Lambda$CDM.

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster. 
The authors would like to thank Andrey Kravtsov and Nelson Padilla
for their useful comments; and Yehuda Hoffman for insightful
conversations on the subject of the Local Group and the Cosmic Web. 
\bibliographystyle{apj}
\bibliography{references}
